### 2020-10-28 Thesis-Chapter2-Background.tex
Finish Chapter 3 draft

Some schemes compensate for the risk of concentrated sensitive information by massively distributing the secret
information. In this arrangement, trust is put in the distrubuted system, not in any single party. Such systems offer
high data availability while making it difficult for attempts to acquire keys to be secret or to subvert access
policies. This approach was introduced in \ac{the-cw1} \cite{goos_oblivious_1996} and has come into its own through the
application of blockchain \cite{phan_key_2017}. These approaches are not as thoroughly explored as trusted-party
\ac{key-escrow}.

>>>>

Some schemes compensate for the risk of concentrated sensitive information by massively distributing the secret
information. In this arrangement, trust is put in the distrubuted system, not in any single party. Such systems offer
high data availability while making it difficult for attempts to acquire keys to be secret or to subvert access
policies. This approach was introduced in \ac{the-cw1} \cite{goos_oblivious_1996} and has modern blockchain
\cite{phan_key_2017} and distributed device \cite{servan_schreiber_jje_2020} variations. These approaches are not as
thoroughly explored as trusted-party \ac{key-escrow}.

### 2020-10-28 Thesis-Chapter3-PolicyMaking.tex
Finish Chapter 3 draft

The \ac{OODAloop} was a developed by Air Force Colonel John Boyd as a description of a successful strategy for
countering opponents in real-time combat \cite{angerman_2004}. Boyd created it in the context of military strategy, but
its ideas have penetrated many other sectors, including cybersecurity, where it serves as a model for structuring
incident response \cite{schneier_future_2014}. There is an emphasis on speed and ``getting inside'' your opponent's
loop. It is illustrated in \myfig{fig-ooda-loop}.

@@

The \ac{OODAloop} serves as a good basis for contending with \acp{wicked-prob} because it has the correct fundamental
structure. It maps very well to the \ac{classical-method} steps of problem definition (orientation), ideation and
analysis (orientation), decision, and action, but it emphasizes the \ac{incrementalism}'s iteration and feedback.
Additionally, while policymaking doesn't share the pace of real-time combat, in other ways the metaphor of facing an
unpredictable opponent in a dynamic environment where every action counts holds up.

The one modification the \ac{OODAloop} needs is unification of the problem definition and analysis steps. This is
Rittel's ``argumentative process in the course of which an image of the problem and of the solution emerges gradually''
\cite{rittel_dilemmas_1973}. \myfig{fig-policy-ooda-loop} illustrates the \ac{OODAloop} modified to serve as a
policymaking strategy.

@@

@@

% Preview it in action in the following chapters

>>>>

The \ac{OODAloop} was a developed by Air Force Colonel John Boyd as a description of a successful strategy for
countering opponents in real-time combat \cite{angerman_2004}. Boyd created it in the context of military strategy, but
its ideas have penetrated many other sectors, including cybersecurity, where it serves as a model for structuring
incident response \cite{schneier_future_2014}. There is an emphasis on fast cycle times and ``getting inside'' your
opponent's loop as a means of overcoming raw power with speed and agility. It is illustrated in \myfig{fig-ooda-loop}.

@@

The \ac{OODAloop} serves as a good basis for contending with \acp{wicked-prob} because it has the correct fundamental
structure. It maps very well to the \ac{classical-method} steps of problem definition (orientation), ideation and
analysis (orientation), decision, and action, but it emphasizes the \ac{incrementalism}'s iteration and feedback.
Additionally, while policymaking doesn't share the pace of real-time combat, in other ways the metaphor holds up. One is
facing an unpredictable opponent in a dynamic environment where every action counts. We cannot overpower
\acp{wicked-prob} through force of reason, but perhaps we can through speed and agility.

The one modification the \ac{OODAloop} needs is unification of the problem definition and analysis steps, as one depends
on the other. This is Rittel's ``argumentative process in the course of which an image of the problem and of the
solution emerges gradually'' \cite{rittel_dilemmas_1973}, illustrated in \myfig{fig-policy-ooda-loop} as a cycle of
``collaborative debate'' between observation and orientation. The modified \ac{OODAloop} incorporates each of the
lessons from \mysec{sec-policy-lessons}.

@@

Recall from \mysec{sec-arg-maps-intro} that \acp{argmap} resulted from the same research that produced the concept of
\acp{wicked-prob}. Though formal research on the technique is thin, \acp{argmap} have proven helpful in simplifying
complex arguments around \acp{wicked-prob} \cite{renton_2007} and in facilitating debate by helpfully slowing down
discussion, depersonalizing conflict, and lending structure and rhythm \cite{dutoit_hypermedia_2006}. This makes them
well suited as a tool for conducting the collaborative debate that helps problem solvers with disparate views narrow in
on a problem definition and concrete proposals on which they can agree.

@@

\section{Summary}

Traditional policymaking typically follows either a rational approach rooted in the scientific method, aiming to be
thorough and complete, or an intuitional approach rooted in evolutionary trial and error, humbly aiming only to take
steps in the right direction. Both approaches have their strengths, but neither is suited to the complex and
controversial nature of so-called ``\acp{wicked-prob}.'' The strategy proposed here relies on the goodwill participation
of all parties, who engage in ongoing research and debate that rejects easy answers, encourages flexible risk-based
solutions, and crystallizes discussion around specific proposals. \Acp{argmap} are one tool that may facilitate this
process. The result from a single iteration is an imperfect step forward based on implementing a particular proposal.
The result from many iterations is the breakdown of the problem into sub-problems---some tame and inevitably some still
wicked. The tame sub-problems can be addressed with the \ac{classical-method}, and the wicked sub-problems, by now
restrained under a sound and agreeable strategy, can be addressed with \ac{incrementalism}.

It is important to note that the same \acp{wicked-prob} is never solved twice, since each one is by definition, unique.
However, changes in technology, culture, and current affairs may render the current strategy insufficient and require
the process to start again. \Acp{wicked-prob} are like history: they don't repeat themselves, but they rhyme. Due to
changing circumstances, solutions past will not work in the future, but lessons learned from the past provide useful
experience.

In the context of \ac{encryption} and \ac{EA}, this means that the outcome of \ac{the-cw1} doesn't hold precedential
power over the debate in the second. It means that re-raising questions about the role of technology is playing society
is legitimate. To follow this proposed strategy would mean that hardline rhetoric doesn't help \cite{ruiz_there_2018}
\cite{geller_2019}, though sincere appeals do \cite{abelson_2015} \cite{intl_2020} \cite{rozenshtein_2019}. Even more
helpful are collaborative efforts involving government, technical, and civil liberties representatives
\cite{committee_decrypting_2018} \cite{group_2019}. Specific proposals around which groups can center discussion,
whether they specify a particular form of \ac{EA} or perhaps especially if they don't, are also a necessary component
\cite{kerr_encryption_2017} \cite{wright_crypto_2018} \cite{phan_key_2017}.

In the remainder of this thesis, I will apply this strategy through the use of \acp{argmap} to document elements of the
debate in \mychap{chap-arguments} and through creation of a threat model against which I analyze one specific proposal
in \mychap{chap-threatmodel}.

### 2020-10-28 Thesis-Glossary.tex
Termify argument maps and remove strategy notes
Finish Chapter 3 draft

\newterm{muddling-through}{muddling through}{
    See ``incrementalism''
}
% End terms

@@

\newabbreviation{USAPATRIOTAct}{USA PATRIOT Act}{Uniting and Strengthening America by Providing Appropriate Tools Required to Intercept and Obstruct Terrorism Act}
\newabbreviation{USAFREEDOMAct}{USA FREEDOM Act}{Uniting and Strengthening America by Fulfilling Rights and Ensuring Effective Discipline Over Monitoring Act}
\newabbreviation{SAFEAct}{SAFE Act}{Security and Freedom Through Encryption Act}
\newabbreviation{PROCODEAct}{Pro-C0DE Act}{Promotion of Commerce On-Line in the Digital Era Act}
\newabbreviation{ENCRYPTAct}{ENCRYPT Act}{Ensuring National Constitutional Rights for Your Private Telecommunications Act}
\newabbreviation{EARNITAct}{EARN IT Act}{Eliminating Abusive and Rampant Neglect of Interactive Technologies Act}
\newabbreviation{LEADAct}{LEAD Act}{Lawful Access to Encrypted Data Act}
\newabbreviation{OODAloop}{OODA loop}{\ii{Observe-Orient-Decide-Act} loop}

>>>>

\newterm{muddling-through}{muddling through}{
    See ``incrementalism''
}

\newterm{argmap}{argument map}{
    A graphical representation of the logical structures and relationships between statements, premises, and
    conclusions, used to disentangle complex arguments used in wicked problems
}
% End terms

@@

\newabbreviation{USAPATRIOTAct}{USA PATRIOT Act}{Uniting and Strengthening America by Providing Appropriate Tools Required to Intercept and Obstruct Terrorism Act}
\newabbreviation{USAFREEDOMAct}{USA FREEDOM Act}{Uniting and Strengthening America by Fulfilling Rights and Ensuring Effective Discipline Over Monitoring Act}
\newabbreviation{SAFEAct}{SAFE Act}{Security and Freedom Through Encryption Act}
\newabbreviation{PROCODEAct}{Pro-C0DE Act}{Promotion of Commerce On-Line in the Digital Era Act}
\newabbreviation{ENCRYPTAct}{ENCRYPT Act}{Ensuring National Constitutional Rights for Your Private Telecommunications Act}
\newabbreviation{EARNITAct}{EARN IT Act}{Eliminating Abusive and Rampant Neglect of Interactive Technologies Act}
\newabbreviation{LEADAct}{LEAD Act}{Lawful Access to Encrypted Data Act}
\newabbreviation{OODAloop}{OODA Loop}{\ii{Observe-Orient-Decide-Act} Loop}
